\section{Job Application Letter}

To Whom It May Concern,

I am excited to be applying for this software development graduate program at Capgemini. I recently graduated from Monash University with a Bachelor's degree (honours) in Electrical and Computer System Engineering and a Bachelor's degree in Science (majoring in Computer Science and Pure Maths). I believe my background, skill set and personality make me a strong candidate for this position, in particular the full-stack development or cloud streams at the Melbourne office, though I am also comfortable with relocation.

I have strong experience with full-stack development, having built a number of large academic and hobby projects. For example, I consulted for, and was the lead software developer of, a cloud application for Monash Health to manage their database of patient-facing projects. This was built using a Node.js backend/React frontend, and it utilised a number of AWS services to manage the cloud architecture. Importantly, this, along with other projects completed, was done in consultation with third-party clients, meaning I know how to communicate and solve technical problems with members from diverse backgrounds. In general, I am passionate about software engineering, having sought out additional opportunities to learn and develop my skillset. I recently began development on a mobile application which required me to learn Golang to write the server logic and API. Expanding my knowledge and thinking creatively as I have had to in these projects is something that I relish, so to have the chance to work alongside like-minded individuals in this program is an exciting prospect.

Beyond academic pursuits, my focus has remained on two things: firstly, to understand how to learn new things quickly, embracing the challenges and responsibilities and seeing it instead as a rewarding opportunity to grow; and secondly, to understand how best to work with others, be it leading from the front or taking guidance from others. So, I believe that I offer a strong union of technical know-how but also the soft skills to communicate these ideas effectively, collaborating with others to quickly become a reliable contributor in this program.

Thank you for considering my application.
