%%%%%%%%%%%%%%%%%
% This is an sample CV template created using altacv.cls
% (v1.7.2, 28 Aug 2024) written by LianTze Lim (liantze@gmail.com), based on the
% CV created by BusinessInsider at http://www.businessinsider.my/a-sample-resume-for-marissa-mayer-2016-7/?r=US&IR=T
%
%% It may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2003/12/01 or later.
%%%%%%%%%%%%%%%%

%% Use the "normalphoto" option if you want a normal photo instead of cropped to a circle
% \documentclass[10pt,a4paper,normalphoto]{altacv}

\documentclass[9pt,a4paper,ragged2e]{altacv}
%% AltaCV uses the fontawesome5 and simpleicons packages.
%% See http://texdoc.net/pkg/fontawesome5 and http://texdoc.net/pkg/simpleicons for full list of symbols.

% Change the page layout if you need to
\geometry{left=1.25cm,right=1.25cm,top=1.2cm,bottom=1.2cm,columnsep=0.8cm}

% The paracol package lets you typeset columns of text in parallel
\usepackage{paracol}


% Change the font if you want to, depending on whether
% you're using pdflatex or xelatex/lualatex
% WHEN COMPILING WITH XELATEX PLEASE USE
% xelatex -shell-escape -output-driver="xdvipdfmx -z 0" mmayer.tex
\ifxetexorluatex
  % If using xelatex or lualatex:
  \setmainfont{Lato}
\else
  % If using pdflatex:
  \usepackage[default]{lato}
  \usepackage{url}
  \usepackage{xcolor}
  \hypersetup{
	colorlinks,
	linkcolor={red!50!black},
	citecolor={blue!50!black},
	urlcolor={blue!80!black}
	}
\fi

% Change the colours if you want to
\definecolor{VividPurple}{HTML}{000000}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{2E2E2E}
\colorlet{heading}{VividPurple}
\colorlet{headingrule}{VividPurple}
\colorlet{accent}{VividPurple}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

\renewcommand{\cvItemMarker}{{\small\textbullet}}
\renewcommand{\cvRatingMarker}{\faCircle}

\begin{document}
\name{Nick Marks}
\tagline{} % need this here even if blank so that it renders
\personalinfo{
	\phone{(+61) 477 971 009}
	\email{\href{mailto:nickmarks00@gmail.com}{nickmarks00@gmail.com}}
	\linkedin{\href{https://www.linkedin.com/in/nickmarks00/}{LinkedIn}}
	\github{\href{https://www.github.com/nickmarks00}{GitHub}}
	\homepage{\href{https://chumbers.io}{Personal Site}}
}

\makecvheader

%% Depending on your tastes, you may want to make fonts of itemize environments slightly smaller
\AtBeginEnvironment{itemize}{\small}

%% Set the left/right column width ratio to 6:4.
\columnratio{0.6}

% Start a 2-column paracol. Both the left and right columns will automatically
% break across pages if things get too long.
\begin{paracol}{2}

	\cvsection{Education}

	\cvevent{BSc Computer Science and Pure Mathematics | \newline BE Electrical and Computer Systems Engineering}{Monash University (WAM: 87.8\%, GPA: 3.88/4.00)}{ 03/2020 - Present }{Melbourne, VIC}
	\begin{itemize}
		\item \textit{Relevant coursework (BSc):} Advanced Algorithms, Data Structures, Operating Systems, AI, Computer Architecture, Linear Algebra, Advanced Calculus, Modelling and Simulation, Group Theory, Real \& Functional Analysis, Graph Theory.
		\item \textit{Relevant coursework (BE):} Embedded Systems, Digital Systems and Logic, Deep Learning, Probability Modelling, FPGA/ASIC Design,  Electrical Circuits, Signals and Systems, Information Theory, Networking, Energy/Power Systems, Web-app Development, Fluid Mechanics.
	\end{itemize}

	\divider

	\cvevent{ Semester Abroad }{Purdue University (WAM: 92.1\%, GPA: 4.00/4.00)}{ 01/2023 - 05/2023 }{West Lafayette, IN}
	\begin{itemize}
		\item \textit{Relevant coursework:} Integrated Circuit Design, Control Systems, Electromagnetics, Artificial Intelligence (AI) and Machine Learning.
	\end{itemize}

	\cvsection{Projects}

	\cvevent{}{Autonomous Navigation through Offline Deep Learning}{07/2023 - Present}{Monash University}
	\begin{itemize}
		\item Researched applications of offline deep learning techniques to autonomously navigate a Penguin Pi bot around varying complexities of road tracks.
		\item Crafted pipeline for training and deploying a model trained via Implicit Q-Learning, using tools like regression analysis and grid-search to optimise trained experts.
	\end{itemize}

	\divider

	\cvevent{}{Rocket Guidance Systems at \href{https://www.purdueorbital.com/}{Purdue Orbital} \faLink}{01/2023 - 05/2023}{West Lafayette, IN}
	\begin{itemize}
		\item Produced control systems on Purdue Orbital's guidance and navigation team for rockets launched by the team in the middle of 2023 as part of Project Icarus.
		\item Crafted state models and Simulink implementations of rocket attitude control and implemented a real-time operating system to interface between the control system, onboard sensors and diagnostic systems.
	\end{itemize}

	\divider

	\cvevent{}{Pollish - A Polling Social Media Platform}{03/2022 - 11/2022}{Melbourne, VIC}
	\begin{itemize}
		\item Produced a full-stack polling mobile application that collated and recommended content from friends that users could vote on. The backend was built using a Django REST framework and the frontend using React Native.
	\end{itemize}

	\divider

	\cvevent{}{Robot-assisted Drone Navigation at \href{https://www.deepneuron.org/}{Monash DeepNeuron} \faLink}{08/2022 - 11/2022}{Monash University}
	\begin{itemize}
		\item Developed a behavioral cloning-based approach to train a AI-assisted drone navigation system capable of flying point-to-point within simulation.
		\item Evaluated the model performance in comparison to a reinforcement-learning approach on a dataset generated by human participants in a small-scale trial ($\sim$30 participants).
	\end{itemize}

	\cvsection{Technical Skills}
	\smallskip
	\begin{itemize}
		\item \textit{Frontend:} JavaScript, React, React Native, NextJS
		\item \textit{Backend:} Django, Node.js, GraphQL, Golang, Java, C\#
		\item \textit{Other languages:} C/C++, Verilog, Python, SQL (MySQL, Postgresql), NoSQL, Redis, Matlab, \LaTeX
		\item \textit{AI and HPC:} Pytorch, TensorFlow, OpenMP, CUDA, CMake, Docker, Pandas, Numpy
		\item \textit{Cloud/DevOps:} AWS (Amplify), Google Cloud (Google App Engine), Linux, Bash
	\end{itemize}

	\cvsection{Languages}

	\cvskill{English}{5}
	% \divider

	\cvskill{German}{4} %% supports X.5 values.

	%% Switch to the right column. This will now automatically move to the second
	%% page if the content is too long.
	\switchcolumn

	\cvsection{Experience}
	\cvevent{CO2 Conversion Project Lead}{\href{https://www.mcarboncapture.com/chemecco}{Monash Carbon Capture and Conversion} \faLink}{08/2021 - 12/2023}{Melbourne, VIC}
	\begin{itemize}
		\item Founded a large-scale research project on the electrochemical reduction of CO2 into fuels in a novel, catalysed flow cell environment.
		\item Self-taught relevant advanced chemistry to grow the team to 10+ students and established relationships with research fellows and professors at my university and abroad.
		\item Our team received US\$250,000 as a top 23 university finalist worldwide in the \href{https://www.xprize.org/prizes/carbonremoval}{XPRIZE Carbon Removal Competition} \faLink.
	\end{itemize}

	\divider

	\cvevent{Lead Software Developer}{\href{https://www.mymi.org.au/}{Monash Young MedTech Innovators} \faLink}{02/2022 - 12/2022}{Melbourne, VIC}
	\begin{itemize}
		\item Led a small team in the production of a cloud-based web-app integrated across university medical platforms and nearby hospital groups.
		\item Designed the app from scratch and oversaw ongoing consultation with the end client regarding requirements and specifications as well as to manage feature releases to production.
	\end{itemize}

	\divider

	\cvevent{Physics Textbook Author}{\href{https://edrolo.com.au/}{Edrolo} \faLink}{10/2019 - 02/2022}{Melbourne, VIC}
	\begin{itemize}
		\item Authored Year 11 and Year 12 physics textbooks and produced digital content used in $\sim$40\% of classrooms across the state of Victoria.
	\end{itemize}

	\cvsection{Competitions}
	\cvevent{}{\href{https://sc21.supercomputing.org/program/studentssc/indyscc/}{ISC21} \faLink \hspace{0.1em} Student Cluster Competition (2nd prize)}{11/2021}{Remote}
	\begin{itemize}
		\item Optimised builds of scientific applications written in Fortran, such as XCompact3D.
		\item Bench-marked builds simulations running on distributed systems, improving parallel performance with OpenMP.
	\end{itemize}

	\divider

	\cvevent{}{A-HUG Cloud Computing Hackathon}{07/2021}{Remote}
	\begin{itemize}
		\item Ported scientific and AI applications to an ARM-based architecture and bench-marked the relevant differences in performance between the ARM architecture and the native one.
	\end{itemize}

	\cvsection{Awards \& Achievements}
	\smallskip
	\begin{itemize}
		\item Dean's honour roll for Faculties of Engineering and Science (2020-2022).
		\item School Captain of Scotch College, conducted post-graduation in a full-time capacity (2019).
		\item Graduated high school with ATAR of 99.95 (top 0.05\% of country). Co-Dux of School, Dux of Literature (2018).
		\item Recipient of \href{https://www.sagse.org.au/}{SAGSE} \faLink \hspace{0.1em} Scholarship for German Language Exchange (2018).
	\end{itemize}

\end{paracol}

\end{document}
